Reasoning about a Capability Machine with Local Capabilities\\ Provably Safe Stack and Return Pointer Management (without OS Support)\\ Technical Appendix Including Proofs and Details

### 2017-11-30 presentations/illustrations/presentation-illustrations.tex
used the inactive adv command in the presentation

\newcommand{\inactadv}[3][]{
  \draw[fill=white] #2 rectangle #3 node[pos=.5] {};
  \draw ($#2 + (3,1.5)$) node[devil,mirrored,minimum size=1cm] {};
  \draw[fill=gray, fill opacity=0.5] #2 rectangle #3 node[pos=.5] {};
  \draw #2 rectangle #3 node[pos=.5] {\footnotesize #1};
}

\newcommand{\actsf}[3][]{
  \draw[fill=white] #2 rectangle #3 node[pos=.5] {};
}

\newcommand{\inactsf}[3][]{
  \draw[fill=white] #2 rectangle #3 node[pos=.5] {};
  \draw[fill=gray, fill opacity=0.5] #2 rectangle #3 node[pos=.5] {};
  \draw #2 rectangle #3 node[pos=.5] {\footnotesize #1};
}

@@

    % attacker calls trusted code again
    \draw<+->[fill=gray!50] (0,4) rectangle (6,7) node[pos=.5] {\footnotesize callee stack frame};
    \begin{onlyenv}<.>
      \draw[fill=white] (0,7) rectangle (6,9) node[pos=.5] {\footnotesize callee (2) stack frame};
      \draw [decorate,decoration={brace,amplitude=10pt,mirror,raise=4pt},yshift=0pt]
        (6.5,7) -- (6.5,16) node[draw=black] (sp1) [black,midway,xshift=0.8cm] {};
      \draw node[right=0cm of sp1] { stack pointer };
    \end{onlyenv}

@@

    % attacker calls trusted code again
    \draw<+->[fill=gray!50] (0,4) rectangle (6,7) node[pos=.5] {\footnotesize callee stack frame};
    \begin{onlyenv}<.-.(1)>
      \draw[fill=white] (0,7) rectangle (6,9) node[pos=.5] {\footnotesize callee (2) stack frame};
      \draw [decorate,decoration={brace,amplitude=10pt,mirror,raise=4pt},yshift=0pt]
        (6.5,7) -- (6.5,16) node[draw=black] (sp1) [black,midway,xshift=0.8cm] {};
      \draw node[right=0cm of sp1] { stack pointer };
    \end{onlyenv}

>>>>

\newcommand{\inactadv}[4][]{
  \ifthenelse{\equal{#1}{}}{
    \draw[fill=white] #2 rectangle #3 node[pos=.5] {};
    \draw ($#2 + (3,1.5)$) node[devil,mirrored,minimum size=1cm] {};
    \draw[fill=white, fill opacity=0.4] #2 rectangle #3 node[pos=.5] {};
    \draw[fill=gray, fill opacity=0.5] #2 rectangle #3 node[pos=.5] {};
    \draw #2 rectangle #3 node[pos=.5] {\footnotesize #4};
  }{
    \draw<#1>[fill=white] #2 rectangle #3 node[pos=.5] {};
    \draw<#1> ($#2 + (3,1.5)$) node[devil,mirrored,minimum size=1cm] {};
    \draw<#1>[fill=white, fill opacity=0.4] #2 rectangle #3 node[pos=.5] {};
    \draw<#1>[fill=gray, fill opacity=0.5] #2 rectangle #3 node[pos=.5] {};
    \draw<#1> #2 rectangle #3 node[pos=.5] {\footnotesize #4};

\newcommand{\actsf}[#4][]{
  \ifthenelse{\equal{#1}{}}{
    \draw[fill=white] #2 rectangle #3 node[pos=.5] {#4};
  }{
   \draw<#1>[fill=white] #2 rectangle #3 node[pos=.5] {#4};
 }
}

\newcommand{\inactsf}[3][]{
  \ifthenelse{\equal{#1}{}}{
    \draw[fill=white] #2 rectangle #3 node[pos=.5] {};
    \draw[fill=gray, fill opacity=0.5] #2 rectangle #3 node[pos=.5] {};
    \draw #2 rectangle #3 node[pos=.5] {\footnotesize #4};
  }{
    \draw<#1>[fill=white] #2 rectangle #3 node[pos=.5] {};
    \draw<#1>[fill=gray, fill opacity=0.5] #2 rectangle #3 node[pos=.5] {};
    \draw<#1> #2 rectangle #3 node[pos=.5] {\footnotesize #4};
  }
}

@@

    % attacker calls trusted code again
%    \draw<+->[fill=gray!50] (0,4) rectangle (6,7) node[pos=.5] {\footnotesize callee stack frame};
    \begin{onlyenv}<+->
      \inactadv{(0,4)}{(6,7)}{callee stack frame}
    \end{onlyenv}
    \begin{onlyenv}<.>
      \draw[fill=white] (0,7) rectangle (6,9) node[pos=.5] {\footnotesize callee (2) stack frame};
      \draw [decorate,decoration={brace,amplitude=10pt,mirror,raise=4pt},yshift=0pt]
        (6.5,7) -- (6.5,16) node[draw=black] (sp1) [black,midway,xshift=0.8cm] {};
      \draw node[right=0cm of sp1] { stack pointer };
    \end{onlyenv}

@@

    % attacker calls trusted code again
    \begin{onlyenv}<+->
    \inactadv{(0,4)}{(6,7)}{callee stack frame}
    \end{onlyenv}
    \begin{onlyenv}<.-.(1)>
      \draw[fill=white] (0,7) rectangle (6,9) node[pos=.5] {\footnotesize callee (2) stack frame};
      \draw [decorate,decoration={brace,amplitude=10pt,mirror,raise=4pt},yshift=0pt]
        (6.5,7) -- (6.5,16) node[draw=black] (sp1) [black,midway,xshift=0.8cm] {};
      \draw node[right=0cm of sp1] { stack pointer };
    \end{onlyenv}
